### 2019-03-22 paper/sex_selection_spacing-ver2.tex
No need to discuss ban's effect

At the other extreme, urban women with eight or more years of education have experienced 
an almost complete reversal of the traditional spacing patterns as a result of falling
fertility and the associated extensive use of sex selection.
Rather than having the next birth sooner as they mostly did before sex selection became 
available, women with either no or one son now have substantially longer spacing than if 
they have two or more sons.
As shown by the increasingly significant deviations in the sex ratio from the natural sex 
ratio, these changes are likely due to increased use of sex selection rather than sudden
reversal in son preference.%
\footnote{
Banning prenatal sex determination has not been able to reverse the use, although it is 
possible that it has slowed the rate of increase.
}
Only the second spell has not seen a reversal despite a substantial increased use of
sex selection, mainly because the average spacing with a first-born boy has increased 
independently by more than nine months.

>>>>

At the other extreme, urban women with eight or more years of education have experienced 
an almost complete reversal of the traditional spacing patterns as a result of falling
fertility and the associated extensive use of sex selection.
Rather than having the next birth sooner as they mostly did before sex selection became 
available, women with either no or one son now have substantially longer spacing than if 
they have two or more sons.
As shown by the increasingly significant deviations in the sex ratio from the natural sex 
ratio, these changes are likely due to increased use of sex selection rather than sudden
reversal in son preference.
Only the second spell has not seen a reversal despite a substantial increased use of
sex selection, mainly because the average spacing with a first-born boy has increased 
independently by more than nine months.
